---
title: "Weather Check Preferences in the United States"
subtitle: Summary Report For the `r params$region` Region
author: 'Author: Kazuki Okubo'
date: "`r format( Sys.Date(), '%A, %B %d, %Y' )`"
output:
  html_document: default
params:
  region:
    label: "Region:"
    value: Mountain
    input: select
    choices: ["East North Central","East South Central", 
              "Middle Atlantic","Mountain", "New England", 
              "Pacific","South Atlantic", "West North Central",
              "West South Central"]
---

```{r setup, include=FALSE}
# define knitr options
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(message=FALSE)

# set any missing values in tables to blank instead of NA
options(knitr.kable.NA="")

# load packages
library(fivethirtyeight)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggthemes)

# load steak survey dataset
data("weather_check", package="fivethirtyeight")

# pick a specific region
sdat <- weather_check %>%
  filter(region == params$region)

```

## Background

In April 2015, Walt Hickey at [538.com](http://fivethirtyeight.com/) published an article entitled ["Where People Go To Check The Weather"](https://fivethirtyeight.com/features/weather-forecast-news-app-habits/). This article utilized survey data collected from 928 people which asked questions on if they typically check the weather on a daily basis and if so, what source they used to check the weather. Additional follow-up questions were asked about which specific websites or apps they used and if they had a smartwatch if they would check the weather on that smartwatch.

## Purpose

The "weather check" dataset that was used for the ["Where People Go To Check The Weather"](https://fivethirtyeight.com/features/weather-forecast-news-app-habits/) article, is available through the R package [`fivethirtyeight`](https://cran.r-project.org/web/packages/fivethirtyeight/index.html). Using this dataset, this article summarizes the weather source preferences for the `r params$region` Region of the United States by gender. 

For our summary presented here, a subset of the original weather check dataset was extracted to only include responses with no missing data and only included respondents from the `r params$region` region of the US. The data subset used for our summary had `r nrow(sdat)` respondents.


## Demographics of Survey Respondents in a Merged Table

This section is provided as an example of how to merge the three demographic summary tables for the `r nrow(sdat)` survey respondents above into a single merged table.

```{r}
tb1 <- sdat %>%
  select(age) %>%
  table() %>%
  prop.table()*100

tb2 <- sdat %>%
  select(female) %>%
  table() %>%
  prop.table()*100

tb3 <- sdat %>%
  select(hhold_income) %>%
  table() %>%
  prop.table()*100

df1 <- as.data.frame(tb1)
df2 <- as.data.frame(tb2)
df3 <- as.data.frame(tb3)

tmp <- merge( data.frame(df1, row.names=NULL),
              data.frame(df2, row.names=NULL),
              by=0, all=TRUE )[-1]

mdf <- merge( data.frame(tmp, row.names=NULL),
              data.frame(df3, row.names=NULL),
              by=0, all=TRUE )[-1]

knitr::kable( mdf, format="html", digits=2,
              col.names=c("Category","%","Category","%","Category","%"), caption="Demographics of Survey Respondents" ) %>%
  kableExtra::kable_styling( bootstrap_options=c("striped","bordered"), full_width=FALSE ) %>%
  add_header_above( c("Ages"=2 ,"Gender"=2, "Income"=2) )
```

## Weather Source Preference by Gender

Finally, here is a breakdown of the `r nrow(sdat)` survey respondents for the `r params$region` region of the US on how they check their daily weather by gender.

```{r}
library(stringr)
ggplot( sdat, aes(x=weather_source, fill=female) ) +
  geom_bar(position="dodge", colour="black") +
  scale_x_discrete( labels=function(x) str_wrap(x, width=20) ) +
  ggtitle( paste0("Weather Source by Gender: ", params$region, " Region") ) +
  xlab("Weather Source Preference") +
  ylab("Number of Respondents") +
  scale_fill_manual( values=c("skyblue","palevioletred"),
                     name="Gender",
                     breaks=c(FALSE,TRUE),
                     labels=c("Male","Female") ) +
  coord_flip() +
  theme_fivethirtyeight()
```
